The Ontological Modal Collapse \\ as a Collapse of the Square of Opposition

### 2016-03-07 Papers/2014/Universalis/ModalCollapse.tex
started with preparation of final version

\documentclass{birkjour}

@@

\usepackage{url}
\usepackage{commands}

@@

All results announced in this note have been 
obtained experimentally using interactive and 
automated theorem provers and model finders
\cite{LEO,Satallax,Isabelle,Coq,Nitpick}.  
The source codes of the experiments, 
as well as the resulting proofs and counter-models, 
are available in
\url{github.com/FormalTheology/GoedelGod/}
in the files \texttt{ModalCollapse.thy} and \texttt{ModalSquareOfOpposition.thy} inside the folder \texttt{Formalizations/Isabelle/Meta} as well as in files inside the folder \texttt{Formalizations/Isabelle/Anderson}.

>>>>

\documentclass{birkmult}

@@

\usepackage{url}
\usepackage{hyperref}
\usepackage[hyphenbreaks]{breakurl}

\usepackage{commands}

@@

\sloppy All results announced in this note have been 
obtained experimentally using interactive and 
automated theorem provers and model finders
\cite{LEO,Satallax,Isabelle,Coq,Nitpick}.  
The source codes of the experiments, 
as well as the resulting proofs and counter-models, 
are available in
\url{github.com/FormalTheology/GoedelGod/}
in the files \url{ModalCollapse.thy} and \texttt{ModalSquareOfOpposition.thy} inside the folder \url{Formalizations/Isabelle/Meta} as well as in files inside the folder \texttt{Formalizations/Isabelle/Anderson}.
